Deeply Virtual Compton Scattering measurement off bound proton

### 2018-07-05 eg6-letters/incoherent/incoherent_prl.tex
Add Stepan's comments

\title{First exclusive Deeply Virtual Compton Scattering measurement off bound nucleon in $^4$He}

@@

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurements in incoherent 
   deeply virtual Compton scattering (DVCS) off $^4$He. The data were 
   accumulated using a 6 GeV longitudinally 
   polarized electron beam incident on a pressurized $^4$He gaseous target 
   placed in front of the CLAS spectrometer in Hall-B at the Thomas Jefferson 
   National Accelerator Facility. The azimuthal angular ($\phi$) dependence of 
   the BSA is studied in a wide range of virtual photon and scattered proton 
   kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound 
   nucleon have been compared with the one on the free proton. In the whole 
   kinematical region of our measurements, the BSA on the bound nucleon is 
   smaller by $20\%$ to $40\%$, indicating possible medium modification 
   on the nucleon's partonic structure. This measurement opens a new 
   opportunity to explore the origin of the EMC effect within the framework of 
   the generalized parton distributions.

@@

Electromagnetic probes have played a major role in advancing our knowledge 
about the structure of the nucleon. While elastic lepton-nucleon measurements have 
taught us about the spatial charge and magnetization distributions 
\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering 
experiments have uncovered the features of momentum sharing between the 
constituents partons, i.e., quarks and gluons \cite{Dokshitzer:1977sg,pdg}.  
With nuclear targets, these measurements have revealed the fact that the 
distribution of quarks in a nucleus is not a simple convolution of 
their distributions within nucleons, an observation known as the ``EMC 
effect''\cite{EMC_first} (for reviews on the topic, see  
\cite{EMC_CERN,EMC_SLAC,EMC_HERMES,EMC_JLab,EMC_John,EMC_mdeium_1,EMC_medium_2}).

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations are set to be revealed through deeply virtual Compton scattering 
(DVCS), i.e., the hard exclusive lepto-production of a real photon, which 
provides access to a three-dimensional imaging of partons within the 
generalized parton distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. Combining these measurements has enabled the first extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of DVCS from the $^{4}$He nucleus are a critical 
step towards providing a similar 3-D pictures of the quark structure of the 
nucleus~\cite{Dupre:2015jha}. In the nuclear case however, two channels are available,
the coherent channel where the nucleus is left intact \cite{Airapetian:2009cga,
Hattawy:2017woc}, and the incoherent channel where the DVCS happens on a nucleon.
The latter, which is the focus of this letter, provides a unique access to the 
modification of the partonic structure of the bound nucleons 
\cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for this measurement as it is 
characterized by a strong binding energy, a relatively high nuclear 
core density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
enough that precise calculation of its structure 
can be performed, making this nucleus the perfect target for our investigation of the 
medium modifications of the nucleon's partonic structure.

@@

FIG.~\ref{fig:diags} illustrates the 
leading-twist handbag diagram for the incoherent DVCS off $^{4}$He. In the 
Bjorken regime, i.e, large virtual photon four-momentum squared 
($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant momentum transfer ($t=(p-p^\prime)^2$), the 
DVCS scattering process can be factorized, leaving the non-perturbative structure 
of the nucleon to be parametrized in terms of four chirally-even GPDs: $H$, 
$E$, $\widetilde{H}$, and $\widetilde{E}$, representing the four helicity-spin 
combinations of the quark-nucleon states \cite{Freund_Collins,Ji_Osborne}.

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. Experimentally, we measure the squared sum of the 
Bethe-Heitler (BH) and the DVCS amplitudes, with the BH the process 
where the real photon is emitted by the incident or the scattered electron 
rather than the nucleon. The BSA arises from the interference 
of these two terms and is directly sensitive to the DVCS amplitude that contain 
the information on the GPDs.  Using a longitudinally polarized electron beam 
(L) and an unpolarized target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

@@

The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
(CEBAF) accelerator at an energy of 6.064 GeV. The data were accumulated over 
40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous $^4$He 
target centered at 64~cm upstream of the CEBAF Large Acceptance Spectrometer 
(CLAS) coordinate center. For DVCS experiments, the CLAS baseline design 
\cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and a 
solenoid magnet. The IC extends the photon detection acceptance of CLAS down 
to a polar angle of 4$^{\circ}$. The 5-Tesla solenoid magnet in the center of 
which the target was located prevented the high-rate low-energy M{\o}ller 
electrons from reaching the CLAS drift chambers by guiding these electrons 
inside a tungsten shield placed around the beam line.

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. The contribution from accidental events, i.e., $e'p'\gamma$ collections 
with particles originating from different electron scatterings,
was evaluated to be of 6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using detector simulation and experimental 
data. From simulation, we calculated the ratio ($R$) of the number of $\pi^0$ 
events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$, 
$R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$. Then in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is the 
number of $ep\rightarrow e'p'\gamma$ ($ep\rightarrow e'p'\pi^0$) experimentally identified. Depending on the 
kinematics, we found this contamination to be of 8 to 10\%.

@@

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$ or $t$) and nine bins in the azimuthal angle ($\phi$).  
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
of the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The main contributions 
to systematic uncertainties on these fits are from the choice of the DVCS 
exclusivity cuts (6\%) and the large binning size (7\%). The systematic uncertainties
sum up to less than 10\% for all data points and thus always remain significantly 
smaller than the statistical errors.

@@

We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
signals at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model uses nuclear spectral function and 
considers mainly off-shell effects. The calculations are carried out at slightly 
different kinematics than our data but still provide important guidance. The 
experimental results appear to have smaller asymmetries especially at low 
$x_{B}$ than the calculations. These differences may arise from nuclear 
effects which are not taken into account in the model, such as long-range 
interactions. On the graph for $-t$ dependence, we show previous measurements 
by the HERMES collaboration \cite{Airapetian:2009cga}, in which only electrons
and photons were measured. Due to the large experimental uncertainties of the HERMES 
points, the two measurements are completely compatible.

@@

%\cite{Hofstadter:1955ae}
\bibitem{Hofstadter:1955ae} R.~Hofstadter and R.~W.~McAllister,
%``Electron Scattering From the Proton,''
Phys.\ Rev.\  {\bf 98}, 217 (1955).
%doi:10.1103/PhysRev.98.217

%\cite{Perdrisat:2006hj}
\bibitem{Perdrisat:2006hj} C.~F.~Perdrisat, V.~Punjabi and M.~Vanderhaeghen,
%``Nucleon Electromagnetic Form Factors,''
Prog.\ Part.\ Nucl.\ Phys.\  {\bf 59}, 694 (2007)
%doi:10.1016/j.ppnp.2007.05.001
%[hep-ph/0612014].

%\cite{Dokshitzer:1977sg}
\bibitem{Dokshitzer:1977sg} Y.~L.~Dokshitzer,
%``Calculation of the Structure Functions for Deep Inelastic Scattering and e+ 
   %e- Annihilation by Perturbation Theory in Quantum Chromodynamics.,''
Sov.\ Phys.\ JETP {\bf 46}, 641 (1977)
[Zh.\ Eksp.\ Teor.\ Fiz.\  {\bf 73}, 1216 (1977)].

%\cite{pdg}
\bibitem{pdg} J.~Beringer {\it et al.} (Particle Data Group), Phys.\ Rev.\ D 
   {\bf 86}, 010001 (2012).

@@

\bibitem{EMC_CERN}
J. Ashman et al. (EMC Collaboration), 
      %Measurement of the ratios of deep inelastic muon-nucleus cross sections 
%on various nuclei compared to deuterium, 
      Phys.\ Lett.\ B\ {\bf 202}, 603 1988.

\bibitem{EMC_SLAC}
J. Gomez et al. (SLAC-E139), 
      %Measurement of the A dependence of deep-inelastic electron scattering, 
      Phys.\ Rev.\ D\ {\bf 49}, 4348 (1994).

\bibitem{EMC_HERMES}
A. Airapetian et al. (HERMES Collaboration), 
      %Nuclear effects on R = $\sigma_{L}/\sigma_{T}$ in deep-inelastic 
%scattering, 
      Phys.\ Lett.\ B\ {\bf 567}, 339 (2003).

\bibitem{EMC_JLab}
J. Seely et al., 
      %New Measurements of the European Muon Collaboration Effect in Very Light 
%Nuclei, 
      Phys.\ Rev.\ Lett.\ {\bf 103}, 202301 (2009).

\bibitem{EMC_John}
J. Arrington et al., 
%A detailed study of the nuclear dependence of the EMC effect and short-range 
%correlations, 
      Phys.\ Rev.\ C\ {\bf 86}, 065204 (2012).

\bibitem{EMC_mdeium_1}
I. Clo\"et et al., 
%Isovector EMC effect explains the NuTeV anomaly, 
Phys.\ Rev.\ Lett.\ {\bf 102}, 252301 (2009).

\bibitem{EMC_medium_2}
I. Clo\"et et al., %Parity-violating DIS and the flavour dependence of the EMC 
%effect, 
Phys.\ Rev.\ Lett.\ {\bf 109}, 182301 (2012).

@@

%\cite{Airapetian:2001yk}
\bibitem{Airapetian:2001yk} A.~Airapetian {\it et al.} [HERMES Collaboration],
%``Measurement of the beam spin azimuthal asymmetry associated with deeply 
   %virtual Compton scattering,''
 Phys.\ Rev.\ Lett.\  {\bf 87}, 182001 (2001)
%doi:10.1103/PhysRevLett.87.182001
%[hep-ex/0106068].

@@

%\bibitem{Airapetian}
%A. Airapetian {\it et al.} [HERMES Collaboration],
%Phys.\ Rev.\ Lett. {\bf 87}, 182001 (2001);
%JHEP {\bf 1207}, 032 (2012);
%JHEP {\bf 1006}, 019 (2010);
%JHEP {\bf 0806}, 066 (2008);
%Phys.\ Lett.\ B {\bf 704}, 15 (2011);
%Phys.\ Rev.\  D {\bf 75}, 011103 (2007);
%JHEP {\bf 0911}, 083 (2009);
%Phys.\ Rev.\ C {\bf 81}, 035202 (2010);
%JHEP {\bf 1210}, 042 (2012).

>>>>

\title{Deeply Virtual Compton Scattering measurement off bound proton}

@@

\date{\today}
\begin{abstract}
 We report the first beam spin asymmetry (BSA) measurements in incoherent 
   deeply virtual Compton scattering (DVCS) off $^4$He. The data were 
   accumulated using a 6 GeV longitudinally 
   polarized electron beam incident on a pressurized $^4$He gaseous target 
   placed in front of the CLAS spectrometer in Hall-B at the Thomas Jefferson 
   National Accelerator Facility. The azimuthal angular ($\phi$) dependence of 
   the BSA is studied in a wide range of virtual photon and scattered proton 
   kinematics. The Q$^2$, $x_B$, and $t$ dependencies of the BSA on the bound 
   proton have been compared with the one on the free proton. In the whole 
   kinematical region of our measurements, the BSA on the bound proton is 
   smaller by $20\%$ to $40\%$, indicating possible medium modification 
   of its partonic structure. This measurement opens a new avenue for 
   studying structure of the bound nucleon and explore the origin of the EMC 
   effect using the framework of the generalized parton distributions.

@@

Electromagnetic probes have played a major role in advancing our knowledge 
about the structure of the nucleon. While lepton-nucleon elastic scattering 
measurements have 
taught us about the spatial charge and magnetization distributions 
\cite{Hofstadter:1955ae,Perdrisat:2006hj}, deep-inelastic scattering 
experiments have uncovered the partonic structure of the nucleon and 
the longitudinal momentum distributions of the 
constituents partons, i.e., quarks and gluons \cite{pdg}.  
With nuclear targets, deeply inelastic lepton scattering measurements 
have revealed the fact that the 
distribution of quarks in a nucleus is not a simple convolution of 
their distributions within nucleons, an observation known as the ``EMC 
effect''\cite{EMC_first} (for reviews on the topic, see  
\cite{Arneodo:1992wf,Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}).

A wealth of information on the structure of hadrons lies in the correlations 
between the momentum and spatial degrees of freedom of the partons. These 
correlations are set to be revealed through deeply virtual Compton scattering 
(DVCS), i.e., the hard exclusive lepto-production of a real photon, which 
provides access to a three-dimensional imaging of partons within the 
generalized parton distributions (GPDs) framework 
\cite{Mueller:1998fv,Ji:1996ek,Ji:1996nm,Radyushkin:1996nd,Radyushkin:1997ki}.   
The free proton DVCS measurement has been the focus of a worldwide effort 
\cite{Stepanyan:2001sm,Airapetian:2001yk,Airapetian:2006zr,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}
involving several accelerator facilities such as Jefferson Lab, DESY and  
CERN. These measurements now enable the extractions of GPDs 
and a 3-D tomography of the free proton \cite{Guidal:2013rya,Dupre:2016mai}.  
New measurements of DVCS from the $^{4}$He nucleus are a critical 
step towards providing a similar 3-D pictures of the quark structure of the 
nucleus~\cite{Dupre:2015jha}. In the nuclear case however, two channels are available,
the coherent channel where the nucleus is left intact \cite{Airapetian:2009cga,
Hattawy:2017woc}, and the incoherent channel where the DVCS happens on a nucleon.
The latter, which is the focus of this letter, provides a unique access to the 
modification of the partonic structure of the bound nucleons 
\cite{simonetta_2,Guzey:2006xi,Guzey:2008fe}. The 
$^{4}$He nucleus is an ideal experimental target for this measurement as it is 
characterized by a strong binding energy, a relatively high nuclear 
core density, and a large EMC effect~\cite{JSeely}. Moreover, it remains simple 
enough that precise calculation of its structure 
can be performed, making this nucleus the perfect target for our investigation of the 
medium modifications of the nucleon's partonic structure.

In the 
Bjorken regime, i.e, large virtual photon four-momentum squared 
($Q^{2}=-q^2=-(k-k^\prime)^2$), and at small invariant momentum transfer ($t=(p-p^\prime)^2$), the 
DVCS scattering process can be factorized, leaving the non-perturbative structure 
of the nucleon to be parametrized in terms of four chirally-even GPDs: $H$, 
$E$, $\widetilde{H}$, and $\widetilde{E}$, representing the four helicity-spin 
combinations of the quark-nucleon states \cite{Freund_Collins,Ji_Osborne}.

@@

In this Letter, we present the first exclusive measurement of the beam-spin 
asymmetry (BSA) in deeply virtual electroproduction of a real photon off a bound 
proton in $^{4}$He. FIG.~\ref{fig:diags} illustrates the 
leading-twist handbag diagram for this process. Experimentally, we measure the squared sum of the 
Bethe-Heitler (BH) and the DVCS amplitudes. The BH process, 
where the real photon is emitted by the incident or the scattered electron 
rather than the nucleon, dominates the cross section at our kinematics. The BSA arises from the interference 
of these two terms and is directly sensitive to the DVCS amplitude that contain 
the information on the GPDs. Using a longitudinally polarized electron beam 
(L) and an unpolarized target (U), the BSA is defined as:
\begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}}.
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+}$($d^{5}\sigma^{-}$) is the photon electroproduction 
differential cross section for a positive (negative) beam helicity.

@@

The experiment (E08-024~\cite{Hafidi:2008pr}) took place in Hall-B of Jefferson 
Lab using the nearly 100\% duty factor, longitudinally-polarized electron beam 
(83$\%$ polarization) from the Continuous Electron Beam Accelerator Facility 
(CEBAF) at an energy of 6.064 GeV. The data were accumulated over 
40 days using a 6-atm-pressure, 292-mm-long, and 6-mm-diameter gaseous $^4$He 
target centered at 64~cm upstream of the CEBAF Large Acceptance Spectrometer 
(CLAS) coordinate center. For DVCS experiments, the CLAS baseline design 
\cite{Mecking:2003zu} is supplemented with an inner calorimeter (IC) and a 
solenoid magnet. The IC extends the photon detection acceptance of CLAS down 
to a polar angle of 4$^{\circ}$. The 5-Tesla solenoid magnet in the center of 
which the target was located prevented the high-rate low-energy M{\o}ller 
electrons from reaching the CLAS drift chambers by guiding these electrons 
inside a tungsten shield placed around the beam line.

@@

%background
The two main backgrounds that contribute to the event sample after the exclusivity cuts are  
due to accidental coincidences and exclusive $\pi^0$ production where one of the photons 
from the $\pi^0$ decay escapes the detection. The contribution from accidental 
events, i.e., $e'p'\gamma$ collections 
with particles originating from different electron scatterings,
was evaluated to be of 6.5\% by selecting events passing all our selection cuts but originating from 
different vertices. The $\pi^0$ contamination was estimated using detector simulation and experimental 
data. From simulation, we calculated the ratio ($R = N^{1\gamma}_{sim}/N^{2\gamma}_{sim}$) 
of the number of $\pi^0$ 
events that are wrongly identified as exclusive $ep\rightarrow e'p'\gamma$ events to the 
number of events correctly identified as exclusive $ep\rightarrow e'p'\pi^0$. Then 
in each kinematical bin and for 
each beam-helicity state, the $\pi^0$-subtracted experimental DVCS events is 
calculated as $N = N^{ep\rightarrow e'p'\gamma}_{exp}- R~N^{ep\rightarrow 
e'p'\pi^0}_{exp}$, where $N^{ep\rightarrow e'p'\gamma}_{exp}$ ($N^{ep\rightarrow e'p'\pi^0}_{exp}$) is the 
number of $ep\rightarrow e'p'\gamma$ ($ep\rightarrow e'p'\pi^0$) experimentally identified. Depending on the 
kinematics, we found this contamination to be of 8 to 10\%.

@@

Due to limited statistics, the data were binned two-dimensionally into 36 bins.  
That is, four bins in one of the kinematical variable of interest ($Q^{2}$, 
$x_{B}$ or $t$) and nine bins in the azimuthal angle ($\phi$).  
FIG.~\ref{fig:alu} presents the measured incoherent $A_{LU}$ as a function of 
$\phi$ in bins of $Q^{2}$, $x_{B}$, and $t$. The curves on the plots are fits 
of the form $\frac{a_{0}~sin(\phi)}{1+ a_{1}~cos(\phi)}$. The main contributions 
to systematic uncertainties on these fits are from the choice of the DVCS 
exclusivity cuts (6\%) and the large bin size (7\%). The systematic uncertainties
sum up to less than 10\% for all data points and thus always remain significantly 
smaller than the statistical errors.

@@

We present in FIG.~\ref{fig:alu90} the dependence of the fitted $A_{LU}$ 
values at $\phi$~=~90$^{\circ}$ on the kinematical variables $Q^2$, $x_{B}$, 
and $t$. Within the given uncertainties, $A_{LU}$ does not indicate a strong 
dependence on $Q^2$. The $x_{B}$ and $t$ dependencies are compared to 
theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. Their model uses nuclear spectral function and 
considers mainly off-shell effects. The calculations are carried out at slightly 
different kinematics than our data but still provide important guidance. The 
experimental results appear to have smaller asymmetries especially at low 
$x_{B}$ than the calculations. These differences may arise from nuclear 
effects which are not taken into account in the model, such as long-range 
interactions. On the graph for $-t$ dependence, we show previous measurements 
by the HERMES collaboration \cite{Airapetian:2009cga}, in which only electrons
and photons were measured. Due to the large experimental uncertainties of the HERMES 
points, the two measurements are completely compatible.

@@

\bibitem{Hofstadter:1955ae} R.~Hofstadter and R.~W.~McAllister,
%``Electron Scattering From the Proton,''
Phys.\ Rev.\  {\bf 98}, 217 (1955).

\bibitem{Perdrisat:2006hj} C.~F.~Perdrisat, V.~Punjabi and M.~Vanderhaeghen,
%``Nucleon Electromagnetic Form Factors,''
Prog.\ Part.\ Nucl.\ Phys.\  {\bf 59}, 694 (2007)

\bibitem{pdg} J.~Beringer {\it et al.} (Particle Data Group), Phys.\ Rev.\ D 
   {\bf 86}, 010001 (2012).

@@

\bibitem{Arneodo:1992wf} 
  M.~Arneodo,
  %``Nuclear effects in structure functions,''
  Phys.\ Rept.\  {\bf 240}, 301 (1994).

\bibitem{Geesaman:1995yd} 
  D.~F.~Geesaman, K.~Saito and A.~W.~Thomas,
  %``The nuclear EMC effect,''
  Ann.\ Rev.\ Nucl.\ Part.\ Sci.\  {\bf 45}, 337 (1995).
  %doi:10.1146/annurev.ns.45.120195.002005

\bibitem{Norton:2003cb} 
  P.~R.~Norton,
  %``The EMC effect,''
  Rept.\ Prog.\ Phys.\  {\bf 66}, 1253 (2003).
  %doi:10.1088/0034-4885/66/8/201

\bibitem{Hen:2016kwk} 
  O.~Hen {\it et al.},
  %``Nucleon-Nucleon Correlations, Short-lived Excitations, and the Quarks Within,''
  Rev.\ Mod.\ Phys.\  {\bf 89}, no. 4, 045002 (2017).

@@

\bibitem{Airapetian:2001yk} A.~Airapetian {\it et al.} [HERMES Collaboration],
%``Measurement of the beam spin azimuthal asymmetry associated with deeply 
   %virtual Compton scattering,''
 Phys.\ Rev.\ Lett.\  {\bf 87}, 182001 (2001)
%doi:10.1103/PhysRevLett.87.182001
%[hep-ex/0106068].

@@
